\chapter*{Statement of Originality}

The thesis contains no material which has been accepted for the award of any other degree or diploma in any university or other tertiary institution and, to the best of my knowledge and belief, contains no material previously published or written by another person, except where due reference has been made in the text. I give consent to the final version of my thesis being made available worldwide when deposited in the University's Digital Repository$^{**}$, subject to the provisions of the Copyright Act 1968.

${}^{**}$Unless an Embargo has been approved for a determined period.\\
\begin{tabular}{l}
\\
\\
\\
\line(1,0){220}\\
Calen Blake, June 2023\\
\end{tabular}

%\clearpage\thispagestyle{empty}

\chapter*{Statement of Collaboration}
I hereby certify that the work embodied in this thesis has been done in collaboration with Dr. Stephan Chalup and Dr. Ali Bakhshi from the School of Engineering, The University of Newcastle, Callaghan, New South Wales, Australia. I have included as part of the thesis a statement clearly outlining the extent of collaboration, with whom under which auspices.

\begin{tabular}{l}
\\
\\
\\
\line(1,0){220}\\
Calen Blake, June 2023\\
\end{tabular}
% \clearpage\thispagestyle{empty}

\chapter*{Statement of Authorship}

By signing below I confirm that the work embodied in this thesis contains following published paper work of which \textbf{Calen Blake} is the leading author. It is worth mentioning that \textbf{Ali Bakhshi} had the active role in the conception and design of this study. Software has been designed by \textbf{Calen Blake} based on the methodologies proposed by \textbf{Ali Bakhshi}.

I included this written statement, endorsed by all authors, attesting to my contribution to the publication.

\begin{tabular}{lr}
& \\
& \\
& \\

\line(1,0){200} & \line(1,0){180} \\
Calen Blake, June 2023 & Stephan Chalup, June 2023 \\
%& \\
& \\
& \\
& \\
\line(1,0){200} \\
Ali Bakhshi,  June 2023
\end{tabular}


% \chapter*{Acknowledgements}



\chapter*{}
\begin{center}
\textit{To\\ my family,\\friends, associates,\\ and those with love in their hearts.}
\end{center}
